\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{url}
\usepackage{balance}

% Page layout
\usepackage[margin=1in]{geometry}

% Spacing
\usepackage{setspace}
\doublespacing

% Captions
\usepackage[labelfont=bf]{caption}

% References
\usepackage{cite}

% TikZ for diagrams (optional)
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows, positioning, fit, backgrounds}

% Colors
\definecolor{ocn-blue}{RGB}{0,82,155}
\definecolor{ocn-light}{RGB}{240,248,255}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=ocn-blue,
    filecolor=ocn-blue,
    urlcolor=ocn-blue,
    citecolor=ocn-blue,
}

% Listings style
\lstset{
    backgroundcolor=\color{ocn-light},
    frame=single,
    frameround=tttt,
    numbers=left,
    stepnumber=1,
    numbersep=5pt,
    tabsize=2,
    breaklines=true,
    breakatwhitespace=true,
    basicstyle=\ttfamily\small,
}

% Title
\title{\textbf{Orchestrating Multi-Agent Collaboration through\\Containerized Agent Runtime}}

% Authors
\author{
    白小心\thanks{中国科学院高能物理研究所} \\
    \texttt{zdzhang@ihep.ac.cn}
    \and
    朵拉 \\
    \texttt{dora@ihep.ac.cn}
}

\date{\today}

\begin{document}

\maketitle

\begin{abstract}
Large Language Model (LLM) based agents are evolving from single-task systems to multi-agent collaborative frameworks. However, existing multi-agent systems typically operate within a single runtime (Single-Runtime Multi-Agent), where all agents share memory, tools, and process space. This architecture suffers from poor isolation, limited scalability, and security vulnerabilities.

We present a containerized agent platform that introduces two key innovations. First, we propose \textbf{Agent-as-Container}: each agent runtime runs in an isolated Kubernetes pod, enabling true isolation, parallel execution, and independent scaling. Second, we design \textbf{Hierarchical Orchestration}: an Orchestrator agent coordinates specialized agent runtimes through a standardized \textbf{Skill} interface, without requiring agents to directly invoke each other.

Our implementation demonstrates that the containerized approach provides significantly faster cold-start compared to VM-based solutions, complete fault isolation (one agent's crash does not affect others), and natural security boundaries aligned with CERT/CNCERT recommendations for agent safety. Experiments show that the Multi-Runtime architecture achieves higher task success rates compared to Single-Runtime approaches, while the Skill-based orchestration substantially reduces cross-agent integration complexity.
\end{abstract}

\input{sections/01_introduction}
\input{sections/02_background}
\input{sections/03_system_design}
\input{sections/04_implementation}
\input{sections/05_evaluation}
\input{sections/06_conclusion}
\input{sections/07_related_work}

% Bibliography
\bibliographystyle{plain}
\bibliography{references}

% Appendix (optional)
\appendix
\input{sections/appendix}

\end{document}
